An New Search for Supernova Remnants in NGC\,6946

### 2019-01-08 ms.tex
Added place holders for all of the figures we expect to have

\begin{figure}
\plotone{rgb_10arcmin_subtracted_2.png}
\caption{An emission-line image of \gal, after continuum subtraction, where R = \ha, G = \sii, and B = \oiii.  The field is 10\arcmin\ square and is oriented N up, E left. \label{fig_overview} }
\end{figure}

\begin{figure}
\plotone{rgb_10arcmin_no_regions.png}
\caption{An emission-line image of \gal, where R = \ha, G = \sii, and B = \oiii.  The field is 10\arcmin\ square and is oriented N up, E left.  [Probably we will show {\bf only} one of these: before or after subtraction.] }
\end{figure}

>>>>

% \begin{figure}
% \plotone{rgb_10arcmin_subtracted_2.png}
%\caption{An emission-line image of \gal, after continuum subtraction, where R = \ha, G = \sii, and B = \oiii.  The field is 10\arcmin\ square and is oriented N up, E left. \label{fig_overview} }
%\end{figure}

\begin{figure}
\plotone{rgb_10arcmin_no_regions.png}
\caption{An emission-line image of \gal, where R = \ha, G = \sii, and B = \oiii.  The field is 10\arcmin\ square and is oriented N up, E left.  {\bf Frank to update} }
\end{figure}

\begin{figure}
\plotone{fig_ha_sub_index.pdf}
\caption{Franks's new figure. This needs to be integrated into the text \label{fig_overview}}
\end{figure}

\begin{figure}
\caption{\bf Place holder for Bill's small area figure. \label{fig_example_image}}
\end{figure}
